Is CSF tracer transporation during 24 hours after infusion explained by diffusion?

### 2019-04-29 tex/rev1/paper.tex
update

\documentclass[12pt,a4paper]{article}
\usepackage{hyperref}
\usepackage{color}
\usepackage{amsmath, amsthm, amssymb, amsfonts, verbatim}
\usepackage{graphicx}
\usepackage[table,x11names]{xcolor}
\usepackage{geometry}
\usepackage{subcaption}
\usepackage[numbers]{natbib}
\usepackage{authblk}
\usepackage{ragged2e}
\title{Assessing paravascular transport in the brain by partial differential equation (PDE) constrained optimization}

@@

\begin{abstract}
The proposed glymphatic system suggests a new mechanism for waste clearance from the brain, and has sparked new research on Alzheimer's disease where one of the defining features
is that metabolic waste accumulate within the brain. The glympahtic hypothesis is still controversial, but experimental investigations in rodents as well as novel MRI investigations in humans indicates the existence of such a system. A proper theoretical foundation 
that explains the fluid transfer mechanisms from first principles is however currently missing.
In particular, a crucial question in the current debate is how much the system accelerate
waste clearance when compared to extracellular diffusion alone. Therefore
we will in this paper evaluate to what extent partial differential constrained optimization methods can be used to identify modeling parameters for glymphatic transport. We assume that the transport can be modeled by a diffusion equation, representing extracellular diffusion and possibly dissipation caused by the glymphatic system. The observations are obtained from novel MRI techniques that
aim to quantify long-term (hours/days) transfer mechanism in the brain.

%The recently proposed glymphatic system propose a new mechanism for waste
%clearance from the brain and has opened for a new paradigm in        
%research on Alzheimer's disease where one of the defining features
%is that metabolic waste accumulate within the brain. The glymphatic system is still controversial and while
%experimental investigations in rodents as well as novel MRI investigations in humans
%provide evidence for the existence of this system, a proper theoretical
%foundation is currently missing from the bio-mechanical point of view. In particular,
%a crucial question in the current debate is how much the system accelerate
%waste clearance when compared to extra-cellular diffusion alone. In this paper,
%we will therefore evaluate to what extent partial differential constrained optimization methods
%can be used to identify modeling parameters for glymphatic transport when we    
%assume that the underlying equation can be represented by a diffusion equation
%representing extra-cellular diffusion and possibly dissipation caused by the glymphatic system.
\end{abstract}
\section{Introduction}
In 2012, ~\citet{iliff2012paravascular} provided evidence for a brain-wide paravascular system, denoted the glymphatic system, which is a pathway for transport of fluids and solutes. It was proposed to have an important metabolic role by providing a pathway for clearance of waste solutes from the brain. Evidence was given that the activity of the glymphatic system increases during  sleep by ~\citet{xie2013sleep}, thus linking sleep to clearance of toxic substances from the brain. The glymphatic system seems to become impaired during aging, and failure of the glymphatic system may play a role in neurodegenerative disease and development of Alzheimer's disease. Evidence for a brain-wide glymphatic system in humans was first obtained in 2015 by \citet{eide2015mri}, and in 2018 \citet{ringstad2018brain} provided evidence that glymphatic function is deteriorated in individuals with dementia, as compared to controls.
Several aspects of the glympahtic system are still debated, for example whether glymphatic transport of solutes is by convective mechanisms or by diffusion.

@@

The work of Sykov{\'a} and Nicholson~\cite{sykova2008diffusion} demonstrated
that diffusion was a governing transport mechanism in the brain at short time-scales and with an estimated order of magnitude $1.0\mathrm{e}{-4} \mathrm{mm\sp{2}/s}$ for large molecules. This is confirmed with diffusion tensor imaging (DTI) where young and healthy subjects have typical diffusion values in white matter around $0.7-0.9\mathrm{e}{-3} \mathrm{mm\sp{2}/s}$ \citet{Helenius194},
while subjects with dementia typically have higher value and variation \cite{goujon2018can}. Of course diffusion coefficients, 
measured by DTI at short time-scales may not be representative for the process on a
longer time-scale, at least if the paravascular pathway plays an important role. The fact that the vascular system occupies around 3\% of the brain volume  \cite{nicholson2001diffusion},
and the paravascular network is substantially smaller potentially renders the paravascular transport  invisible at the short time-scales of a DTI acquisition while it may still be effective on longer time scales.

@@

\subsection{MRI Data}
\begin{figure}
\includegraphics[width=0.95\textwidth]{PatID-new-100.png} 
\caption{Shows the percentage change in T1 signal unit ratios from baseline at different observation times. The colorbar was restricted to the range $(0,100)$. }
\label{fig1} 
\end{figure}

\begin{figure}
\includegraphics[width=0.95\textwidth]{Zoom-PatID.png} 
\caption{Shows the percentage change in T1 signal unit ratios from baseline at different observation times in the slice (marked red in the left panel) used in the subsequent analysis. The color bar was restricted to the range $(0,100)$. }
\label{fig2} 
\end{figure}
Figure~\ref{fig1} shows distribution of MRI-contrast%CSF tracer
, as a percentage change in T1 signal unit ratios, see also~\cite{ringstad2018brain} for further information on the imaging procedure.   
Our data (not all shown) consist of a total of 10 MRI observations, including a baseline MRI taken before the contrast was injected. The observation points are distributed over 5 observations within 1-2 hours after injection, a single observation in the timeframes 2-4 hours, 6-9 hours, 24 hours and 48 hours. 
Figure~\ref{fig2} shows the region selected for our computations. 
The software Freesurfer \cite{Dale1999179, FischlLiuDale, spf2007, reuter:robreg10} was used to segment and align each of the observations, which made it possible to estimate voxelwise signal increase.

@@

\begin{figure}
\centering
\includegraphics[width=0.70\textwidth]{T1function.png} 
\caption{Shows the  function defined in \eqref{scaledmagnetization} where the white region indicates $T_1$ values for white matter, the grey region indicates $T_1$ values for grey matter, the blue region indicates $T_1$ values for CSF.  }
\label{figureF} 
\end{figure}

\subsection{Diffusion tensor imaging}
In addition to the T1 and T2 weighted sequences described above we have also obtained diffusion tensor imaging to assess the apparent diffusion 
coefficients on short time-scales. Images are shown in Figure~\ref{figuredti} where the largest diffusion coefficient (shown in 
red in the middle figure) is shown to be around $1.0\mathrm{e}{-3}  \mathrm{mm^2/s}$. We remark that we have not included possible anisotropy, shown in 
the right-most image in Figure~\ref{figuredti} and that these images show the apparent diffusion coefficient for free water molecules (18 Da).      
The diffusivity of the Gadovist (600 Da) \cite{MGadobutrol} was estimated to be similar to the diffusion coefficient of Gd-DPTA (550 Da) \cite{MGgDPTA}. This is due to the fact that both molecules have similar mass, and based on Stoke-Einstein equation should also have similar diffusion coefficients. The free diffusion coefficient for Gd-DPTA was estimated in \citet{GdDPTA-DIFFUSION} to be $3.8\mathrm{e}{-4}\mathrm{mm\sp{2}/s}$.
The fractional anisotropy is defined as 
\begin{equation}
FA\sp{2} =  \frac{3}{2} \frac{ (\lambda_1 - MD )\sp{2} +(\lambda_2 - MD )\sp{2} +(\lambda_3 - MD )\sp{2}}{\lambda\sp{2}_1 + \lambda\sp{2}_2  +\lambda\sp{2}_3 },
\end{equation}
with the mean diffusivity $MD$ defined as 
\begin{equation}
MD = \frac{\lambda_1 +\lambda_2 +\lambda_3 }{3}.
\end{equation}
In these equations $\lambda_i$ denotes the eigenvalues of the diffusion tensor.
\begin{figure}
\centering
\includegraphics[width=0.75\textwidth]{DTI-zoom.png} 
\caption{The left panel shows the anatomical map. The middle panel shows the apparent diffusion coefficients (ADC) obtained from DTI. The right panel shows the computed fractional anisotropy (FA) from the DTI.}
\label{figuredti} 
\end{figure}

@@

The mesh construction was patient-specific and used the MRI of a patient diagnosed with idiopathic normal pressure hydrocephalus (iNPH). The software Freesurfer was used to segment and create the polyhedral surfaces of the white and grey matter. Then the T2 weighted MRI \cite{ringstad2018brain} was used to segment the CSF compartment surrounding the cerebral and the lateral ventricles. CGAL \cite{cgal:rty-m3-18b} was used to combine the polyhedral surfaces and to construct the mesh. The computational requirement for the resulting mesh was significant, therefore two submeshes was also constructed, see Figure~\ref{Fig::Mesh}.
\begin{figure}
\centering
\includegraphics[scale=0.2]{mesh.png} 
\caption{The leftmost image A) shows the mesh created from the baseline MR image with 3 domains, while the rightmost image  B) shows the mesh created from the baseline MR image with 2 domains. The blue domain corresponds to CSF domain, $\Omega_{CSF}$, the purple domain corresponds to grey matter,  $\Omega_{GM}$, and the white domain corresponds to white matter, $\Omega_{WM}$. }
\label{Fig::Mesh}
\end{figure}
The 3 domain mesh in Figure~\ref{Fig::Mesh} A, consists of 244318 tetrahedral cells and 22057 vertices, while the 2 domain mesh (without the CSF compartment) Figure~\ref{Fig::Mesh} B consists of 335589 tetrahedral cells and 73002 vertices.

@@

\begin{figure}
\centering
\includegraphics[scale=0.18]{Convergence-plot.png}   
\caption{Convergence plots of the diffusion coefficients, boundary conditions and functional with respect to different $\alpha$ and $\beta$ values. } 
\label{convergence}
\end{figure}

@@

\begin{figure}
\centering
\includegraphics[scale=0.21]{boundary_control.png}  
\caption{ Displays plots over time for a selection of points at the boundary of $\Omega_1$ with different regularization parameters and number of timesteps $k$. The left panel shows the legend for the plot over time, together with the selection of points. The middle panel shows the average boundary value $g$ for different regularization parameter with $k=10$. The right panel shows the average boundary value $g$ for different regularization parameter with $k=40$.  }
\label{boundarycontrol}
\end{figure}

@@

\begin{figure}
\centering
\includegraphics[scale=0.4]{noise-12.png}  
\caption{The upper row shows the manufactured observation, A) Shows the manufactured observation at time-point 24 with no noise added. B) Shows the manufactured observation at time-point 24 with noise amplitude of 0.15. C) Shows the manufactures observation at time-point 24 with noise amplitude of 0.3. The lower row shows the results with optimized parameter obtained with $\alpha=0.0001$, $\beta=1.0$ and $k=20$. D) Shows the resulting state given the observation in A. E)  Shows the resulting state given the observation in B .F) Shows the resulting state given the observation in C. }
\label{12hourswithnoise}
\end{figure}

\begin{figure}
\centering
\includegraphics[scale=0.4]{noise-24.png}
\caption{The upper row shows the manufactured observation, A) Shows the manufactured observation at time-point 24 with no noise added. B) Shows the manufactured observation at time-point 24 with noise amplitude of 0.15. C) Shows the manufactures observation at time-point 24 with noise amplitude of 0.3. The lower row shows the results with optimized parameter obtained with $\alpha=0.0001$, $\beta=1.0$ and $k=20$. D) Shows the resulting state given the observation in A. E)  Shows the resulting state given the observation in B .F) Shows the resulting state given the observation in C.  }
\label{24hourswithnoise}
\end{figure}

@@

\begin{figure}
\centering
\includegraphics[width=0.95\textwidth]{different.png} 
\caption{Row A) shows the observation at times 2 hours, 6 hours, 24 hours and 48 hours after the first observation with contrast. Row B) shows the corresponding states with the relaxation parameters $\alpha=0.01$ and $\beta=0.01$ and $k=48$.   Row C) shows the corresponding states with the relaxation parameters $\alpha=1.0\mathrm{e-4}$ and $\beta=1.0$ and $k=48$
 Row D) shows the corresponding states with the relaxation parameters $\alpha=1.0\mathrm{e-6}$ and $\beta=0.1$ and $k=48$. The color-bar was restricted to the range $ \lbrace 0 ,0.5 \rbrace$. }
\label{Fig::realdata}
\end{figure}

\begin{figure}
\centering
\includegraphics[width=0.95\textwidth]{Statecomparison36h-pinta.png} 
\caption{ Displays the states for different regularization parameters after 36 hours for $k=48$.}
\label{statecomparison}
\end{figure}

>>>>

\documentclass[12pt,a4paper]{article}
\usepackage{hyperref}
\usepackage{color}
\usepackage{amsmath, amsthm, amssymb, amsfonts, verbatim}
\usepackage{graphicx}
\usepackage[table,x11names]{xcolor}
\usepackage{geometry}
\usepackage{subcaption}
\usepackage[numbers]{natbib}
\usepackage{authblk}
\usepackage{ragged2e}
\title{
	Is CSF tracer transporation during 24 hours after infusion explained by diffusion?
}

@@

\begin{abstract}
The proposed glymphatic system suggests a new mechanism for waste clearance from the brain, and has sparked new research on Alzheimer's disease where one of the defining features
is that metabolic waste accumulate within the brain. The glympahtic hypothesis is still controversial, but experimental investigations in rodents as well as novel MRI investigations in humans indicates the existence of such a system. A proper theoretical foundation 
that explains the fluid transfer mechanisms from first principles is however currently missing.
In particular, a crucial question in the current debate is how much the system accelerate
waste clearance when compared to extracellular diffusion alone. Therefore
we will in this paper evaluate to what extent partial differential constrained optimization methods can be used to identify modeling parameters for glymphatic transport. We assume that the transport can be modeled by a diffusion equation, representing extracellular diffusion and possibly dissipation caused by the glymphatic system. The observations are obtained from novel MRI techniques that
aim to quantify long-term (hours/days) transfer mechanism in the brain. 
\kam{have not looked at the abstract yet}

%The recently proposed glymphatic system propose a new mechanism for waste
%clearance from the brain and has opened for a new paradigm in        
%research on Alzheimer's disease where one of the defining features
%is that metabolic waste accumulate within the brain. The glymphatic system is still controversial and while
%experimental investigations in rodents as well as novel MRI investigations in humans
%provide evidence for the existence of this system, a proper theoretical
%foundation is currently missing from the bio-mechanical point of view. In particular,
%a crucial question in the current debate is how much the system accelerate
%waste clearance when compared to extra-cellular diffusion alone. In this paper,
%we will therefore evaluate to what extent partial differential constrained optimization methods
%can be used to identify modeling parameters for glymphatic transport when we    
%assume that the underlying equation can be represented by a diffusion equation
%representing extra-cellular diffusion and possibly dissipation caused by the glymphatic system.
\end{abstract}
\section{Introduction}
In 2012, ~\citet{iliff2012paravascular} provided evidence for a brain-wide paravascular system, denoted the glymphatic system, which is a pathway for transport of fluids and solutes. It was proposed to have an important metabolic role by providing a pathway for clearance of waste solutes from the brain. Evidence was given that the activity of the glymphatic system increases during  sleep by ~\citet{xie2013sleep}, thus linking sleep to clearance of toxic substances from the brain. The system proposes that 
the interplay between the cerebrospinal fluid (CSF) and the CSF-filled channels surrounding the vasculature of the brain, traditionally called Wirchow-Robin spaces, are crucial to  
facilitate this process.  
These findings are important because both Alzheimer's and Parkinson's diseases are associated with accumulation of metabolic waste products in within various parts of the brain. 
In \cite{iliff2013brain} a procedure for  investigate paravascular transport was proposed  and tested in a rat's brain. The procedure involved injecting a 
MRI-contrast into the CSF and image the transportation of the MRI-constrast over a few hours after the injection.  
The procedure was extended to humans for the first time 
in 2015 by \citet{eide2015mri} where MRI images where acquired during 48 hours after the injection and quantified in a region-specific manner in 2018 \citet{ringstad2018brain} in individuals with dementia and controls. Overall, the MRI-contrast transportation  showed a centripetal and delayed pattern in individuals with dementia as compared with controls~\citet{ringstad2018brain}.

The glympahtic system is controversial as the theory proposes that a significant part of the waste disposal system is driven by convection rather than diffusion. As such
the system may be much more efficient than if driven by diffusion alone. The theory would also explain why the lymphatic system which elsewhere in our body is crucial for
removing metabolic waste is not present in the brain even though the brain has a high metabolism; namely that the brain has its own specialized system. 
The properties of the extracellular diffusion are well-known due to seminal work of Nicholson and colleagues, see  
~\cite{sykova2008diffusion} for an overview, and is fundamental to for  diffusion tensor imaging (DTI). 
It has been shown that diffusion coefficients in young and healthy subjects in white matter is around $0.7-0.9\mathrm{e}{-3} \mathrm{mm\sp{2}/s}$ \citet{Helenius194},
while subjects with dementia typically have higher value and variation \cite{goujon2018can}. 
For larger molecules such as albumin (65-70 kDa) \citet{cserr1971physiology} estimated that transport by diffusion of a distance of 1 cm would require more than a hundred hours
and is therefore deemed to slow for the high demands of the brain.  
The crux of the glymphatic system is as such the fact that conventional DTI imaging is well explained by the traditional view of transportation by extracellular diffusion. 
However, the paravascular compartments are small, probably less than the vascular compartment that occupy around 3\% of the brain volume. As such, 
due to its small volume, the paravascular compartment may be dominated by the extracellular compartment at short time-scales, while still being a
significant contributor on longer time scales.

%Several aspects of the glympahtic system are still debated, for example whether glymphatic transport of solutes is by convective mechanisms or by diffusion.

@@

@@

\subsection{MRI Data}
\begin{figure}
\includegraphics[width=0.95\textwidth]{../PatID-new-100.png} 
\caption{Shows the percentage change in T1 signal unit ratios from baseline at different observation times. The colorbar was restricted to the range $(0,100)$. }
\label{fig1} 
\end{figure}

\begin{figure}
\includegraphics[width=0.95\textwidth]{../Zoom-PatID.png} 
\caption{Shows the percentage change in T1 signal unit ratios from baseline at different observation times in the slice (marked red in the left panel) used in the subsequent analysis. The color bar was restricted to the range $(0,100)$. }
\label{fig2} 
\end{figure}
Figure~\ref{fig1} shows distribution of MRI-contrast%CSF tracer
, as a percentage change in T1 signal unit ratios, see also~\cite{ringstad2018brain} for further information on the imaging procedure.   
Our data (not all shown) consist of a total of 10 MRI observations, including a baseline MRI taken before the contrast was injected. The observation points are distributed over 5 observations within 1-2 hours after injection, a single observation in the timeframes 2-4 hours, 6-9 hours, 24 hours and 48 hours. 
Figure~\ref{fig2} shows the region selected for our computations. 
The software Freesurfer \cite{Dale1999179, FischlLiuDale, spf2007, reuter:robreg10} was used to segment and align each of the observations, which made it possible to estimate voxelwise signal increase.

@@

\begin{figure}
\centering
\includegraphics[width=0.70\textwidth]{../T1function.png} 
\caption{Shows the  function defined in \eqref{scaledmagnetization} where the white region indicates $T_1$ values for white matter, the grey region indicates $T_1$ values for grey matter, the blue region indicates $T_1$ values for CSF.  }
\label{figureF} 
\end{figure}

\subsection{Diffusion tensor imaging}
In addition to the T1 and T2 weighted sequences described above we have also obtained diffusion tensor imaging to assess the apparent diffusion 
coefficients on short time-scales. Images are shown in Figure~\ref{figuredti} where the largest diffusion coefficient (shown in 
red in the middle figure) is shown to be around $1.0\mathrm{e}{-3}  \mathrm{mm^2/s}$. We remark that we have not included possible anisotropy, shown in 
the right-most image in Figure~\ref{figuredti} and that these images show the apparent diffusion coefficient for free water molecules (18 Da).      
The diffusivity of the Gadovist (600 Da) \cite{MGadobutrol} was estimated to be similar to the diffusion coefficient of Gd-DPTA (550 Da) \cite{MGgDPTA}. This is due to the fact that both molecules have similar mass, and based on Stoke-Einstein equation should also have similar diffusion coefficients. The free diffusion coefficient for Gd-DPTA was estimated in \citet{GdDPTA-DIFFUSION} to be $3.8\mathrm{e}{-4}\mathrm{mm\sp{2}/s}$.
The fractional anisotropy is defined as 
\begin{equation}
FA\sp{2} =  \frac{3}{2} \frac{ (\lambda_1 - MD )\sp{2} +(\lambda_2 - MD )\sp{2} +(\lambda_3 - MD )\sp{2}}{\lambda\sp{2}_1 + \lambda\sp{2}_2  +\lambda\sp{2}_3 },
\end{equation}
with the mean diffusivity $MD$ defined as 
\begin{equation}
MD = \frac{\lambda_1 +\lambda_2 +\lambda_3 }{3}.
\end{equation}
In these equations $\lambda_i$ denotes the eigenvalues of the diffusion tensor.
\begin{figure}
\centering
\includegraphics[width=0.75\textwidth]{../DTI-zoom.png} 
\caption{The left panel shows the anatomical map. The middle panel shows the apparent diffusion coefficients (ADC) obtained from DTI. The right panel shows the computed fractional anisotropy (FA) from the DTI.}
\label{figuredti} 
\end{figure}

@@

The mesh construction was patient-specific and used the MRI of a patient diagnosed with idiopathic normal pressure hydrocephalus (iNPH). The software Freesurfer was used to segment and create the polyhedral surfaces of the white and grey matter. Then the T2 weighted MRI \cite{ringstad2018brain} was used to segment the CSF compartment surrounding the cerebral and the lateral ventricles. CGAL \cite{cgal:rty-m3-18b} was used to combine the polyhedral surfaces and to construct the mesh. The computational requirement for the resulting mesh was significant, therefore two submeshes was also constructed, see Figure~\ref{Fig::Mesh}.
\begin{figure}
\centering
\includegraphics[scale=0.2]{../mesh.png} 
\caption{The leftmost image A) shows the mesh created from the baseline MR image with 3 domains, while the rightmost image  B) shows the mesh created from the baseline MR image with 2 domains. The blue domain corresponds to CSF domain, $\Omega_{CSF}$, the purple domain corresponds to grey matter,  $\Omega_{GM}$, and the white domain corresponds to white matter, $\Omega_{WM}$. }
\label{Fig::Mesh}
\end{figure}
The 3 domain mesh in Figure~\ref{Fig::Mesh} A, consists of 244318 tetrahedral cells and 22057 vertices, while the 2 domain mesh (without the CSF compartment) Figure~\ref{Fig::Mesh} B consists of 335589 tetrahedral cells and 73002 vertices.

@@

\begin{figure}
\centering
\includegraphics[scale=0.18]{../Convergence-plot.png}   
\caption{Convergence plots of the diffusion coefficients, boundary conditions and functional with respect to different $\alpha$ and $\beta$ values. } 
\label{convergence}
\end{figure}

@@

\begin{figure}
\centering
\includegraphics[scale=0.21]{../boundary_control.png}  
\caption{ Displays plots over time for a selection of points at the boundary of $\Omega_1$ with different regularization parameters and number of timesteps $k$. The left panel shows the legend for the plot over time, together with the selection of points. The middle panel shows the average boundary value $g$ for different regularization parameter with $k=10$. The right panel shows the average boundary value $g$ for different regularization parameter with $k=40$.  }
\label{boundarycontrol}
\end{figure}

@@

\begin{figure}
\centering
\includegraphics[scale=0.4]{../noise-12.png}  
\caption{The upper row shows the manufactured observation, A) Shows the manufactured observation at time-point 24 with no noise added. B) Shows the manufactured observation at time-point 24 with noise amplitude of 0.15. C) Shows the manufactures observation at time-point 24 with noise amplitude of 0.3. The lower row shows the results with optimized parameter obtained with $\alpha=0.0001$, $\beta=1.0$ and $k=20$. D) Shows the resulting state given the observation in A. E)  Shows the resulting state given the observation in B .F) Shows the resulting state given the observation in C. }
\label{12hourswithnoise}
\end{figure}

\begin{figure}
\centering
\includegraphics[scale=0.4]{../noise-24.png}
\caption{The upper row shows the manufactured observation, A) Shows the manufactured observation at time-point 24 with no noise added. B) Shows the manufactured observation at time-point 24 with noise amplitude of 0.15. C) Shows the manufactures observation at time-point 24 with noise amplitude of 0.3. The lower row shows the results with optimized parameter obtained with $\alpha=0.0001$, $\beta=1.0$ and $k=20$. D) Shows the resulting state given the observation in A. E)  Shows the resulting state given the observation in B .F) Shows the resulting state given the observation in C.  }
\label{24hourswithnoise}
\end{figure}

@@

\begin{figure}
\centering
\includegraphics[width=0.95\textwidth]{../different.png} 
\caption{Row A) shows the observation at times 2 hours, 6 hours, 24 hours and 48 hours after the first observation with contrast. Row B) shows the corresponding states with the relaxation parameters $\alpha=0.01$ and $\beta=0.01$ and $k=48$.   Row C) shows the corresponding states with the relaxation parameters $\alpha=1.0\mathrm{e-4}$ and $\beta=1.0$ and $k=48$
 Row D) shows the corresponding states with the relaxation parameters $\alpha=1.0\mathrm{e-6}$ and $\beta=0.1$ and $k=48$. The color-bar was restricted to the range $ \lbrace 0 ,0.5 \rbrace$. }
\label{Fig::realdata}
\end{figure}

\begin{figure}
\centering
\includegraphics[width=0.95\textwidth]{../Statecomparison36h-pinta.png} 
\caption{ Displays the states for different regularization parameters after 36 hours for $k=48$.}
\label{statecomparison}
\end{figure}
